---
title: "AirBnB Zero Inflation Poisson Model"
author: "Maggie Upjohn"
date: "11/24/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=TRUE}
library(readr)
library(dplyr)
library(mosaic)
library(ggplot2)
library(tidyverse)
library(gridExtra) 
library(MASS)
library(lme4)
library(knitr)
library(pscl)
```

#1. Reading the datasets:
```{r, include=TRUE}
listing <- read.csv("/home/rstudio/courses/2019-20-semester1-stats-316/Project/Kshitij-Rayan-Maggie/listings.csv")
dim(listing) #6716  106
reviews <- read.csv("/home/rstudio/courses/2019-20-semester1-stats-316/Project/Kshitij-Rayan-Maggie/reviews.csv")
dim(reviews) # 142341      6
```
#Cleaning variables:
```{r}
#Variables parsing
##Price
listing$price <- as.character(listing$price)
listing$finalprice <- parse_number(listing$price)
##host_response_rate
listing$host_response_rate <- as.character(listing$host_response_rate)
listing$host_response_rate<- with(listing, str_sub( host_response_rate,1,-2))
listing$host_response_rate<-as.integer(listing$host_response_rate)
##security_deposit
listing$security_deposit <- as.character(listing$security_deposit)
listing$security_deposit <- parse_number(listing$security_deposit)
##cleaning_fee and extra people\
listing$cleaning_fee <- as.character(listing$cleaning_fee)
listing$cleaning_fee <- parse_number(listing$cleaning_fee)

```

Host Response Time

```{r, echo=FALSE}
listing %>% 
    group_by(room_type) %>% 
    summarise_(n = ~n()) %>% 
    mutate(prop = prop.table(n))

review_scores_ratinghist <-listing %>%
  ggplot(mapping= aes(review_scores_rating)) +
           geom_histogram()
review_scores_ratinghist
```
```{r}
finalpricehist <-listing %>%
  ggplot(mapping= aes(finalprice)) +
           geom_histogram()
finalpricehist
```


Host Response Rate

```{r, echo=FALSE}
favstats(listing$host_response_rate)

host_response_ratehist <-listing %>%
  ggplot(mapping= aes(host_response_rate)) +
           geom_histogram()
host_response_ratehist

```

```{r}
airbnbzipmodel <- listing %>%
  filter(!is.na(host_response_rate))
```

```{r}
airbnbreviews <-zeroinfl(formula = number_of_reviews_ltm ~ review_scores_rating + finalprice+ room_type | host_response_rate, data = airbnbzipmodel)

summary(airbnbreviews)

exp(coef(airbnbreviews)
```

```{r}
poisAIRBNB <- glm(number_of_reviews_ltm ~ review_scores_rating + finalprice+ room_type, family=poisson, data=airbnbzipmodel)
summary(poisAIRBNB)

vuong(poisAIRBNB,airbnbreviews)
```


For the properties that had at least one person leave a review, the average number of reviews increases by 2.39% with each additional increase in review score rating, given that you are comparing properties with comparable prices and room type.

For the properties that had at least one person leave a review, the average number of reviews increases by 0.1% with each additional increase in price, given that you are comparing properties with comparable review scores and room types.


Overdispersion parameter





